\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-07-27 syntax.tex
Reply the comments.

$$ 
\Rule[name=Sig Proj Beta]
{\goodSig{\Gamma}{\sigma}{n} 
\quad \goodType{\Gamma}{A}{}
\quad \goodSeal{\Gamma}{f}{\sigma}{A}
\quad \goodType{\Gamma, A}{T}{i}}
{\goodSig{\Gamma}{p_1\nu \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv \sigma}{n}
\\ \goodType{\Gamma}{p_1\nu' \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv A}{}
\\ \goodSeal{\Gamma}{p_f\nu \  (\nu^+ \ \sigma \ \{f\} \ T) \equiv f}{\sigma}{A}
\\ \goodType{\Gamma, p_1\nu' \ \sigma}{p_2\nu \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv T}{}
}\YZ{p_f nu' or p_f nu? In the syntax figure, you only have p_f nu, I think.}
$$

@@

For notation clarity, we will sometimes use $sf'$ to emphasize that we
consider that the seal $\goodSeal{\Gamma}{s}{\sigma}{A}$ as a term
$\goodTerm{\Gamma, \cC \sigma}{sf'~s}{A[\pi_1]}$.\YZ{sf' seems unnecessary, since sf' s ad s are the same?}\EDJreply{Yes. Technically it is pretty unnecessary. It is just a bit weird to have $\goodTerm{\Gamma, \cC \sigma}{s}{A[\pi_1]}$ and $\goodSeal{\Gamma}{s}{\sigma}{A}$ at the same time because it is one derivation but turns out to be two judgements, for intrinsically typed. I can also remove ``sf'' if you don't find it weird. I initially having ``sf'' to just *emphasize* ``sf s'' should be considered as a term  and ``s'' a sealing}\YZreply{
  I'm still confused about the difference among s, sf s and sf' s.
  I thought s and sf' s were technically the same; they are both terms of type A[pi1] in a context that contains cC sigma.
  I thought sf s was different because it is a substitution.
}
Notation "sf"
(used in \ruleref{Compile}) is defined as the substitution $\goodSub{\Gamma,
\cC \sigma}{(sf~s) := (\pi_1, sf'~s)}{\Gamma, A}$.

>>>>

$$ 
\Rule[name=Sig Proj Beta]
{\goodSig{\Gamma}{\sigma}{n} 
\quad \goodType{\Gamma}{A}{}
\quad \goodSeal{\Gamma}{f}{\sigma}{A}
\quad \goodType{\Gamma, A}{T}{i}}
{\goodSig{\Gamma}{p_1\nu \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv \sigma}{n}
\\ \goodType{\Gamma}{p_1\nu' \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv A}{}
\\ \goodSeal{\Gamma}{p_f\nu \  (\nu^+ \ \sigma \ \{f\} \ T) \equiv f}{\sigma}{A}
\\ \goodType{\Gamma, p_1\nu' \ \sigma}{p_2\nu \ (\nu^+ \ \sigma \ \{f\} \ T) \equiv T}{}
}\YZ{p_f nu' or p_f nu? In the syntax figure, you only have p_f nu, I think.}\EDJreply{p_f nu, I don't have p_f nu' here. the prime is just for specifying we are taken out the abstraction result.}
$$

@@

For notation clarity, we will sometimes use $sf'$ to emphasize that we
consider that the seal $\goodSeal{\Gamma}{s}{\sigma}{A}$ as a term
$\goodTerm{\Gamma, \cC \sigma}{sf'~s}{A[\pi_1]}$.\YZ{sf' seems unnecessary, since sf' s ad s are the same?}\EDJreply{Yes. Technically it is pretty unnecessary. It is just a bit weird to have $\goodTerm{\Gamma, \cC \sigma}{s}{A[\pi_1]}$ and $\goodSeal{\Gamma}{s}{\sigma}{A}$ at the same time because it is one derivation but turns out to be two judgements, for intrinsically typed. I can also remove ``sf'' if you don't find it weird. I initially having ``sf'' to just *emphasize* ``sf s'' should be considered as a term  and ``s'' a sealing}\YZreply{
  I'm still confused about the difference among s, sf s and sf' s.
  I thought s and sf' s were technically the same; they are both terms of type A[pi1] in a context that contains cC sigma.
  I thought sf s was different because it is a substitution.
}\EDJreply{You are absolutely right. s and sf' s are techincally the same. sf s is a substitution.
  About s and sf' s, I can say that, I don't allow something like $\goodSeal{\Gamma}{sf'~s}{\sigma}{A}$. The reason I don't allow it is only notational consideration. 
  I mean technically we can consider them the same. I can just remove all the appearances of sf' if you want and find it less confusing.
}
Notation "sf"
(used in \ruleref{Compile}) is defined as the substitution $\goodSub{\Gamma,
\cC \sigma}{(sf~s) := (\pi_1, sf'~s)}{\Gamma, A}$.
